### 2017-05-12 Publications/Original Software Publications/Science of Computer Programming/reply letter/letter.tex
added answers to Felipe's questions
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{quote}
\textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: haven't we explained that in {\bf Limitations} subsection on page 6?}}
\end{quote}

@@

  \begin{quote}
  \textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: Shall we reference your work about verifying multithread ANSI-C programs?}}
  \end{quote}

@@

  \begin{quote}
  \textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: I didn't get it. Did you?}}
  \end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: does he mean C++? Shall we reference the paper from ECBS 2013 about ESBMC++?}}
\end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: don't we explain that on Functionalities section? Any ideia what else we could add?}}
\end{quote}

@@

    \begin{quote}
    \textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: To be honest, I didn't get it. Do you think this is correct? Could professor Ricardo Pereira help us answer this question appropriately?}}
    \end{quote}

@@

    \begin{quote}
    \textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: which reference would you suggest to use here?}}
    \end{quote}

@@

    \begin{quote}
    \textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: what would be the next step to reduce the number of thread interleavings? Improve MPOR?}}
    \end{quote}

>>>>

\begin{quote}
\textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: haven't we explained that in {\bf Limitations} subsection on page 6?} The reviewer wants to know more details about the type of bugs that we have found in the benchmarks. May I ask you to take a look at our journal paper? I think we describe the type of bugs there. }
\end{quote}

@@

  \begin{quote}
  \textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: Shall we reference your work about verifying multithread ANSI-C programs? Yes, please. Also reference our journal paper about esbmc-gpu.}}
  \end{quote}

@@

  \begin{quote}
  \textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: I didn't get it. Did you? Can you cite our TACAS 2014 paper? I suggest you to read that paper which briefly explains our memory model. Then you can properly reply to the reviewer and cite that paper.}}
  \end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: does he mean C++? Shall we reference the paper from ECBS 2013 about ESBMC++? Yes, please. Mention that we support C++ and cite our ECBS 2013 paper.}}
\end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: don't we explain that on Functionalities section? Any ideia what else we could add? The problem is that we have page limit, right? Can you please mail the editor and check if we can exceed the page limit to properly handle the reviewer comments?}}
\end{quote}

@@

    \begin{quote}
    \textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: To be honest, I didn't get it. Do you think this is correct? Could professor Ricardo Pereira help us answer this question appropriately? Can you please check this with Isabela? Isabela had worked quite hard on the experimental evaluation and examples of our papers.}}
    \end{quote}

@@

    \begin{quote}
    \textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: which reference would you suggest to use here? Add a reference to some book on GPU. You can also briefly explain the term and then cite the reference.}}
    \end{quote}

@@

    \begin{quote}
    \textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: what would be the next step to reduce the number of thread interleavings? Improve MPOR? You can mention that we intend to use Abstract Interpretation to further reduce the model and the number of threads. Then you can cite our TACAS 2017 paper}}
    \end{quote}
